

\documentclass[]{deedy-resume-openfont}


\begin{document}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{} {Pritha D Narayanappa}{  \\
\href{mailto:pritha.narayanappa@gmail.com}{pritha.narayanappa@gmail.com} | 805.453.1220
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.35\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{University of \\ California \\ Santa Barbara}
\descript{MS
IN
COMPUTER
SCIENCE}
\location{Dec 2016 | Santa Barbara,CA \\ GPA: 4.0 / 4.0}\\
\textbf{Research Asst. SAND Lab \\ Advisor:Prof. Ben Y. Zhao }} \\
Conc. in Security, Machine Learning \\
\sectionsep
\subsection{PES Institute of Technology}
\prithadescript{BE
in
Information
Science}
\location{June 2011 | Bangalore, India}

\location{GPA: 9.47 / 10.0 }
Merit Scholarship all 4 years (Top 5/150) \\
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/pritha90}{\custombold{pritha90}} \\
LinkedIn://  \href{https://www.linkedin.com/in/PrithaDN}{\custombold{PrithaDN}} \\
Quora://  \href{https://www.quora.com/profile/Pritha-D-Narayanappa}{\custombold{Pritha-D-Narayanappa}}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Graduate}
Applied Machine Learning \\
Distributed Systems \\
Applied Parallel Computing \\
Cryptography–Theory and Applications \\
Data and Knowledge Bases \\
\sectionsep

\subsection{Undergraduate}
Operating Systems \\
Data Mining \\
Computer Security\\
Computer Networks\\
Algorithms Design \& Analysis\\
Database Systems\\
\sectionsep

\subsection{Publications}
{\fontsize{9}{11}\selectfont
Face
recognition
using
a
trichotomic
combination
of
SVD,
DF-LDA
and
LPP;
ICCAE
2010,
Singapore. \\
Face
Recognition
by
Feedforward
Neural
Network
using
Laplacian
of
Gaussian
filter
and
Singular
Value
Decomposition;
ICIIC
2010,
Bangalore,
India.
}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}

\location{Over 5000 lines:}
\textbullet{} C++
\location{Over 1000 lines:}
\textbullet{} Python
\textbullet{} Java     \textbullet{} C \\
\textbullet{} Android \textbullet{} JavaScript \\
\location{Familiar:}
\textbullet{}Rails \textbullet{} iOS  \textbullet{} MySQL \\ \textbullet{} MongoDB\textbullet{} CSS \textbullet{}Redis
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.63\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
Over \textbf{8 years} of industry experience in \textbf{Software Development}.         \\
\runsubsection{Google}
\location{Nov 2019 - Present| Sunnyvale, CA}
NetInfra team(C++):
Lead for design, development of features in the Data Center Network controller, mainly dealing with the Top of Racks.
\sectionsep

\runsubsection{Cisco Systems}
\location{Apr 2019 - Nov 2019 | San Jose, CA}
Design, development of zero-touch provisioning in Branch and Colocation solution of a Network Function Virtualisation solution.
\sectionsep

\runsubsection{Riverbed Technology}
\location{Jan 2017 – Apr 2019 | San Francisco, CA}
\location{(Software Development Intern, June 2016 – Sep 2016)}
Network Performance Management Platform team(Python, C):
Involved in the design, development and support of:
\vspace{\topsep}
\begin{tightemize}
\item Operating System and manageability software running on the SteelCentral product line,
 mainly dealing with Storage devices support, Network interfaces, SNMP support.
\item Infrastructure tools and systems aimed at stress testing SteelCentral AppResponse. 
\item Tools to manage virtualization infrastructure (VMware and AWS) 
\end{tightemize}
\sectionsep

\runsubsection{Citrix
Systems}
\location{July 2011 – Aug 2015 | Bangalore, India}
\begin{tightemize}
\item NetScaler
Networking
Team
(
C)
Part of a three member team
involved
in
the
development
of
the
Large
Scale
Network
Address
Translation
(LSN)
feature
for
protocols
TCP,
UDP,
ICMP.
\item NetScaler
GUI
Team
(
JavaScript,
HTML)
Developed a
web-based
mobile
application (Android
and
iOS)
for
monitoring
a
NetScaler
Load
balancer.
\end{tightemize}
\sectionsep

\runsubsection{Cisco Systems}
\descript{| Software Development Intern}
\location{Jan 2010 – June 2010 | Bangalore, India}
Tools written in Python to aid Network Engineers in the task of migrating routers from the IOS to XR Operating System.
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\prithasubsection{Solution for secure, anonymous, group communication on OSNs}
Developed a system (Android app, Chrome Plugin) that
allows
a
group
of
users
to
share
a
Twitter
account
or
Facebook
page,
without
sharing
the
account
password.
\sectionsep

\prithasubsection{User
Behavior
Modeling
on
Financial
Message
Boards}
 Crawled
data
from
the
InvestorsHub
website(53K users and 5.6M posts).
Employed
Machine
Learning
techniques:
PCA,
Random
Forest,
K-Means,
hierarchical
clustering,
to
identify,
cluster
and
infer
roles
of
users
exhibiting
similar
behavior.

\sectionsep

\prithasubsection{Implementation of Raft Consensus protocol}
Implemented the Raft consensus protocol in Java. In a distributed system, it supports leader election and runtime configuration changes like addition and deletion of nodes.
\sectionsep

\prithasubsection{Parallel KMeans using CUDA
}
Implemented K-Means Clustering in C using CUDA. Observed maximum speedup of 104X.

\section{Awards} 
\begin{tabular}{rll}
2011	     & National  & Google
India
Women
in
Engineering
Award finalist\\
2010 & 2/300 & Selected to attend International Summer\\  & & University Program, HEIG-VD, Switzerland\\
\end{tabular}

\end{minipage} 
\end{document}
